Untitled

### 2020-11-24 ms/manuscript.Rmd
Update pgls analysis

Desiccation tolerance tended to increase with decreasing environmental water potential for both gametophytes and sporophytes (Fig. 6).
These trends were significant when analyzed using PGLS for sporophytes (*P* = 0.036) but not gametophytes (*P* = 0.123; Appendix S5).

@@

Vegetative DT was a key innovation linked to the rise of early land plants, but is largely limited to non-vascular groups such as bryophytes and algae in modern plants.
Filmy ferns have received considerable attention over the years for their remarkable reversion to vegetative DT in the sporophyte phase (e.g., Shreve, 1911; Proctor, 2003; Cea et al., 2014).
Yet, no previous study to our knowledge has evaluated parallel physiology of sporophytes and gametophytes of filmy ferns in relation to DT.
Here, we present the first comparisons of physiological parameters between generations within filmy ferns in a phylogenetic comparative framework.

>>>>

Desiccation tolerance tended to increase with VPD for both gametophytes and sporophytes (Fig. 6).
These trends were significant when analyzed using PGLS for sporophytes (*P* = 0.036) but not gametophytes (*P* = 0.123; Appendix S5).

@@

Vegetative DT was a key innovation linked to the rise of early land plants, but is largely limited to non-vascular groups such as bryophytes and algae in modern plants.
Filmy ferns have received considerable attention over the years for their remarkable reversion to vegetative DT in the sporophyte phase [\eg, @Shreve1911; @Proctor2003; @GarcesCea2014].
Yet, no previous study to our knowledge has evaluated parallel physiology of sporophytes and gametophytes of filmy ferns in relation to DT.
Here, we present the first comparisons of physiological parameters between generations within filmy ferns in a phylogenetic comparative framework.
